---
title: "R Development Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R Development Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a simple vignette to demonstrate the functions that are available in the DevelExample package. The purpose of this package is to demonstrate the process of adding code to an R function. The full tutorial "Adding code to an R package" can be found at the [Campbell lab website](camplab.net) under the "Articles" tab.

Let's first load the library:

```{r setup}
library(DevelExample)
```

Next we can run our function with default parameters:

```{r hello}
hello()
```

We can also run the same function but without all of the exclamation marks:

```{r hello2}
hello(withExcitement = FALSE)
```

It is usually a good idea to show the session information to help with reproducibility:

```{r session}
sessionInfo()
```

To calculate the euclidean distance between two vectors, we can use the `euclideanDist` function. In this example we will generate two random vectors from normal distributions with two different means and calculate the distance between them:

```{r dist}
set.seed(12345)
v1 <- rnorm(10000, mean = 1)
v2 <- rnorm(10000, mean = 2)
res <- euclideanDist(v1, v2, verbose = FALSE)
res
```

The `set.seed` function is used for the random number generator and ensures the same vectors will be produced each time for reproducibility.

